---
title: "COVID-19 Analysis"
author: "Your name goes here"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---


```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, include=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(here)
library(skimr)
library(janitor)
library(httr)
library(readxl)
library(vroom)
```




CDC COVID-19 Public Use Data

I used the [CDC Covid-19 Case Surveillance Data](https://data.cdc.gov/Case-Surveillance/COVID-19-Case-Surveillance-Public-Use-Data/vbim-akqf). 


```{r, cache=TRUE}

url <- "https://data.cdc.gov/api/views/vbim-akqf/rows.csv?accessType=DOWNLOAD"

covid_data <- vroom::vroom(url) %>% # If vroom::vroom(url) doesn't work, use read_csv(url)
  clean_names()


```


Using the data gathered, I created graphs that shows the % death rate by ge group, sex, and whether the patient had co-morbidities or not

```{r covid_challenge, echo=FALSE, out.width="100%"}


covid_data %>% 
  filter(!medcond_yn %in% c("Missing", "Unknown")) %>% 
  filter(!sex %in% c("Missing", "Unknown", "Other", NA)) %>% 
  filter(!age_group %in% c("Missing", "Unknown", "Other")) %>% 
  mutate(death_rate_binary = case_when(death_yn == "Yes" ~ 1, 
                                       TRUE ~ 0)) %>%
  group_by(age_group, sex, medcond_yn) %>% 
  summarise(death_percent = mean(death_rate_binary)*100) %>% 
  ungroup() %>% 
  mutate(comorbidities = case_when(medcond_yn == "Yes" ~ "With Comorbidities", 
                            TRUE ~ "Without Comorbidities")) %>% 
  ggplot() +
  geom_bar(aes(death_percent,  age_group), stat = "identity", fill = "#4863A0", alpha = 0.8) + 
  geom_text(aes(death_percent, y = age_group, label = round(death_percent, 1)), hjust = -0.1,  size = 3) + 
  facet_grid(comorbidities ~  sex) +
    labs(
    
    x = "", 
    y = "", 
    title = "Covid death % by age group, sex and presence of co-morbidities"
    
  ) + 
   theme_bw() +
   theme(plot.title = element_text(size=11)) 
   


```


Using the data gathered, I created graphs that shows the % death rate by ge group, sex, and whether the patient had co-morbidities or not
```{r .height = 12}


# by age group, sex, and whether the patient had  admited to Intensive Care Unit (ICU) or not.
covid_data %>% 
  mutate(death_rate_binary = case_when(death_yn == "Yes" ~ 1, 
                                       TRUE ~ 0)) %>%
  group_by(age_group, sex, icu_yn) %>% 
  summarise(death_percent = mean(death_rate_binary)*100) %>% 
  ungroup() %>% 
  filter(!icu_yn %in% c("Missing", "Unknown")) %>% 
  filter(!sex %in% c("Missing", "Unknown", "Other", NA)) %>% 
  filter(!age_group %in% c("Missing", "Unknown", "Other")) %>% 
  mutate(icu_admitted = case_when(icu_yn == "Yes" ~ "Admitted to ICU", 
                            TRUE ~ "NO ICU")) %>% 
  ggplot() +
  geom_bar(aes(death_percent,  age_group), stat = "identity", fill = "#E77471", alpha = 0.8) + 
  geom_text(aes(death_percent, y = age_group, label = round(death_percent, 1)), hjust = -0.1,  size = 3) + 
  facet_grid(icu_admitted ~  sex) + 
  labs(
    
    x = "", 
    y = "", 
    title = "Covid death % by age group, sex and whether patient was admitted to ICU"
    
  ) + 
   theme_bw() + 
     theme(plot.title = element_text(size=11))
  


```


Besides the graphs, make sure your code is easy to read and understand-- imagine if you revisit this six months from now. you should be able to follow what you were doing!


